---
title: "SpatialTests"
author: "Paul M"
date: "11/17/2020"
output: pdf_document
---

Playing around with cluster detection on networks

Load some packages

```{r   libraries}
library("RColorBrewer") 
library("png")
library("ggraph")
library("networkD3")
library("animation")
library("maps")

library("geosphere")
library("RColorBrewer")
```

Globals...
```{r, globals}
set.seed(597)
SizeOfOurNetwork <- 20
ProbOfAVertex <- 0.25
```


Build a random network
```{r network}

RandomEdges <- function (x){
  x <- runif(1)<ProbOfAVertex
  return (x)
}

RemoveSelfLoops <- function(x){
  if (x[1]==x[2])  x[3] <- 0
  return (x)
}

BuildRandomNetwork <- function(NetSize){
  MyNodes <- seq(1,SizeOfOurNetwork)

  x <- seq(1, SizeOfOurNetwork)
  y <- x
  
  MyEdges <- expand.grid(x = x, y = y)
  # make it undirected
  MyEdges2 <- MyEdges[MyEdges[,1]<MyEdges[,2],]

  EdgePresent <- rep(0,length(MyEdges2[,1]))
  EdgePresent <- apply(as.matrix(EdgePresent),MARGIN=1,FUN=RandomEdges)

  MyEdges3 <- cbind(MyEdges2,EdgePresent)
  
  MyEdges4 <- MyEdges3[MyEdges3[,3]==1,]

  ThisNetwork <- graph_from_data_frame(d=as.data.frame(MyEdges4),vertices=as.data.frame(MyNodes), directed=F) 
  
  return (ThisNetwork)
}




# make it undirected
#MyEdges2 <- MyEdges[MyEdges[,1]<MyEdges[,2],]
# remove self-self edges
#MyEdges3 <- t(apply(MyEdges,MARGIN=1,FUN=RemoveSelfLoops))
# remove missing edges


```


Plot the network using the igraph library
```{r  plot}
library("igraph")

#net <- graph_from_data_frame(d=as.data.frame(MyEdges4),vertices=as.data.frame(MyNodes), directed=F) 

net <- BuildRandomNetwork(SizeOfOurNetwork)
class(net)
net 

plot(net) 

# there are all sorts of pretty options
plot(net, edge.arrow.size=.2, edge.curved=0,
     vertex.color="cyan", vertex.frame.color="#555555",
     vertex.label.cex=.7,vertex.size=20) 


# Compute node degrees (#links) and use that to set node size:
#deg <- degree(net)
sum(E(net)==1)
V(net)$size <- 20 #deg*3
l <- layout_with_fr(net)
plot(net, layout=l, vertex.color="cyan",)


```

Edges, vertices and entire mx can be accessed as follows: (nice tutorial at https://kateto.net/wp-content/uploads/2016/01/NetSciX_2016_Workshop.pdf)
```{r, eval=FALSE}
E(net)
V(net)
net[]
```

Add attributes to the network, vertices, or edges as follows
```{r}
for (i in 1:length(V(net)))
  V(net)$MyAttribute[i] <- runif(1)
vertex_attr(net)
plot(net, edge.arrow.size=.5, vertex.label.color="black", vertex.label.dist=1.5,
vertex.size=4+10*V(net)$MyAttribute)
```

A network diameter is the longest geodesic distance (length of the shortest path between two nodes)
in the network. In igraph, diameter() returns the distance, while get_diameter() returns the
nodes along the first found path of that distance.
Note that edge weights are used by default, unless set to NA.
```{r}
diameter(net, directed=F, weights=NA)
diameter(net, directed=F)

diam <- get_diameter(net, directed=F)
diam
plot(net, layout=l, vertex.color="cyan",)
```

Distances between nodes:
```{r}
distances(net,v=V(net)[1],to=V(net)[2])
distances(net,v=(V(net)==9),to=(V(net)==18))
distances(net,v=(V(net)==2),to=(V(net)==17))

distances(net,v=V(net),to=V(net))
DM <- distances(net,v=V(net),to=V(net))


```

Calcluating Moran's (global) I
```{r, MoransI}

MoransI <- function(DistanceMx, NodeAttributes){
  NoOfNodes <- length(DistanceMx[1,])
  WeightSum <- 0
  MoranSum <- 0
  DenomSum <- 0
  AttributeMean <- mean(NodeAttributes)
  cat("\nAttribute mean= ",AttributeMean)
  for (i in 1:NoOfNodes){
    DenomSum <- DenomSum + (NodeAttributes[i]-AttributeMean) * (NodeAttributes[i]-AttributeMean) 
    for (j in 1:NoOfNodes){
      if ( i != j){
        ThisDist <- DistanceMx[i,j]
        if (ThisDist == 1) # neighbors only
        {
          WeightSum <- WeightSum + ThisDist
          MoranSum <- ThisDist * (NodeAttributes[i]-AttributeMean) * (NodeAttributes[j]-AttributeMean)
        }
        # V(net)$MyAttribute
      }
    }
  }
  MoransI <- NoOfNodes * MoranSum / ( DenomSum * WeightSum)
}

cat("\nMorans-I: ",MoransI(DM,V(net)$MyAttribute),"    expectation= ",-1/(length(V(net)$MyAttribute)-1))

```

Test it out...
```{r, Tests}
for (k in 1:10){
  net <- BuildRandomNetwork(SizeOfOurNetwork)
  for (i in 1:length(V(net)))
    V(net)$MyAttribute[i] <- runif(1)
  vertex_attr(net)
  DM <- distances(net,v=V(net),to=V(net))
  plot(net, edge.arrow.size=.5, vertex.label.color="black", vertex.label.dist=1.5,
  vertex.size=4+10*V(net)$MyAttribute)
  
  cat("\nMorans-I: ",MoransI(DM,V(net)$MyAttribute),"    expectation= ",-1/(length(V(net)$MyAttribute)-1))

}

```

Assigning spatially correlated node labels
```{r, Correlated}
# Pick a node at random
CentralNode <- sample(1:SizeOfOurNetwork,1)
cat("\nCentralNode: ",CentralNode)
# label it and all its neighbors 1, and everything else 0.
V(net)$MyAttribute <- 0
V(net)$MyAttribute[CentralNode] <- 1
for (i in 1:SizeOfOurNetwork){
  if (distances(net,CentralNode,i) == 1){
    V(net)$MyAttribute[i] <- 1
  }
}

  plot(net, edge.arrow.size=.5, vertex.label.color="black", vertex.label.dist=1.5,
  vertex.size=4+10*V(net)$MyAttribute)
  
  cat("\nMorans-I: ",MoransI(distances(net,v=V(net),to=V(net)),V(net)$MyAttribute),"    expectation= ",-1/(length(V(net)$MyAttribute)-1))

```


* Random Other things

Node degrees
The function degree() has a mode of in for in-degree, out for out-degree, and all or total for
total degree.
```{r}
deg <- degree(net, mode="all")
plot(net, vertex.size=deg*2)
hist(deg, breaks=1:vcount(net)-1, main="Histogram of node degree")
```



Erdos-Renyi random graph model
(???n??? is number of nodes, ???m??? is the number of edges).
```{r}
er <- sample_gnm(n=100, m=200)
plot(er, vertex.size=6, vertex.label=NA)
```

Barabasi-Albert preferential attachment model for scale-free graphs
(n is number of nodes, power is the power of attachment (1 is linear); m is the number of edges
added on each time step)
```{r}
ba <- sample_pa(n=100, power=1, m=1, directed=F)
plot(ba, vertex.size=6, vertex.label=NA)
```



Rewiring a graph
each_edge() is a rewiring method that changes the edge endpoints uniformly randomly with a
probability prob.
```{r}
set.seed((876))
ba.rewired <- rewire(ba, each_edge(prob=0.1))
lay <- layout_with_fr(ba.rewired)
plot(ba.rewired, vertex.size=10, vertex.label=NA, vertex.color="blue")
plot(ba.rewired, vertex.size=10, vertex.label=NA, vertex.color="blue",layout=lay)
```
